Comparative vaccine effectiveness of ChAdOx1 versus BNT162b2 in Health and Social Care workers in England

### 2021-09-02 analysis/report/draft-manuscript.Rmd
limits

  plot_riskdiff <-
    ggplot(riskdifference)+
    geom_hline(aes(yintercept=0), colour='black')+
    geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
    # geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
    facet_grid(cols=vars(outcome_descr))+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    coord_cartesian(ylim=limits = c(-5, 5))+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Risk difference\nper 1000",
      colour=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y.left = element_line(colour = "black"),

>>>>

  plot_riskdiff <-
    ggplot(riskdifference)+
    geom_hline(aes(yintercept=0), colour='black')+
    geom_step(aes(x=tstop, y=diff*1000), colour='orchid4')+
    # geom_rect(aes(xmin=lag(tstop, 1, 0), xmax=tstop, ymin=diff.ll*1000, ymax=diff.ul*1000), alpha=0.1, colour="transparent", fill='orchid4')+
    facet_grid(cols=vars(outcome_descr))+
    scale_x_continuous(
      limits = c(0, NA),
      breaks = seq(0,7*52,by=14),
      expand = expansion(0)
    )+
    scale_y_continuous(
      expand = expansion(0),
      sec.axis = dup_axis(name="Lower risk after \n <- BNT162b2 / ChAdOx1 ->", breaks = NULL)
    )+
    coord_cartesian(ylim= c(-5, 5))+
    scale_colour_brewer(type="qual", palette="Set1", na.value="grey")+
    scale_fill_brewer(type="qual", palette="Set1", guide="none", na.value="grey")+
    labs(
      x=NULL,
      y="Risk difference\nper 1000",
      colour=NULL
    )+
    theme_bw()+
    theme(
      panel.border = element_blank(),
      axis.line.y.left = element_line(colour = "black"),
